Community-Conditioned Language Models

### 2021-05-14 paper/paper.tex
legend
reword

\newcommand{\modelboxplot}[3]{
  \addplot+[
    boxplot={draw position=#3, box extend=0.3}, 
    draw=#2, mark=*, mark options={fill=#2, scale=0.5}, solid, fill=#2!10,
    area legend] 
    table [y=#1] {floats/comm.csv};
}
\begin{figure}[t]
\begin{tikzpicture}
  \begin{axis}[name=ig,
    height=7cm,width=8cm,
    boxplot/draw direction=x, axis x line*=bottom, axis y line*=left,y axis line style={opacity=0},
    %xmax=1.6,
    ylabel=$l_c$, xlabel=$\IG_{M_j}$,
    legend style={font=\tiny,at={(1,1)},anchor=north east}, legend columns=2
    ]
    \addplot[thin, red, samples=2] coordinates {(1,-0.5)(1,3.5)};
    \foreach \lc in {0, ..., 3}{
      \modelboxplot{lstm-3-\lc_ig}{violet}{\lc+0.2}
      \modelboxplot{transformer-3-\lc_ig}{teal}{\lc-0.2}
    \legend{,LSTM, Transformer}
    }
  \end{axis}
  \begin{axis}[name=ppl,
    anchor=north west,at={($(ig.south west)-(0,1.1cm)$)},
    width=8cm, height=2.5cm, 
    boxplot/draw direction=x, axis x line*=bottom, hide y axis,
    xlabel=$\Ppl_{M_j}$,
    ]
    \modelboxplot{lstm-3_ppl}{violet}{0.2}
    \modelboxplot{transformer-3_ppl}{teal}{-.2}
  \end{axis}
\end{tikzpicture}
\caption{
   Average model performance by community. 
   Also see table 1 in the supplementary materials
   for a tabular version of these results with community names.
}
\label{fig:comm-stratified-box}
\end{figure}

@@

We can characterize the quality\jp{performance} of the LMCC with a confusion matrix
$C$, defined by $C_{ij} = P(c=c_i \mid m)$ for a given (test set) message $m$ 
from community $c_j$.
\[C_{ij} = \avg_{m\in M_j}P(c=c_i \mid m)\]
We observe that the diagonal dominates the matrix: the LMCC generally finds the right community for a message (\cref{fig:confusion}).

>>>>

\newcommand{\modelboxplot}[3]{
  \addplot+[
    boxplot={draw position=#3, box extend=0.3}, 
    draw=#2, mark=*, mark options={fill=#2, scale=0.5}, solid, fill=#2!10,
    area legend] 
    table [y=#1] {floats/comm.csv};
}
\begin{figure}[t]
\begin{tikzpicture}
  \begin{axis}[name=ig,
    height=7cm,width=8cm,
    boxplot/draw direction=x, axis x line*=bottom, axis y line*=left,y axis line style={opacity=0},
    %xmax=1.6,
    ylabel=$l_c$, xlabel=$\IG_{M_j}$,
    legend style={font=\tiny,at={(1,1)},anchor=north east}, legend columns=2
    ]
    \addplot[thin, red, samples=2] coordinates {(1,-0.5)(1,3.5)};
    \foreach \lc in {0, ..., 3}{
      \modelboxplot{lstm-3-\lc_ig}{violet}{\lc+0.2}
      \modelboxplot{transformer-3-\lc_ig}{teal}{\lc-0.2}
    \legend{,LSTM, Transformer}
    }
  \end{axis}
  \begin{axis}[name=ppl,
    anchor=north west,at={($(ig.south west)-(0,1.1cm)$)},
    width=8cm, height=2.5cm, 
    boxplot/draw direction=x, axis x line*=bottom, hide y axis,
    xlabel=$\Ppl_{M_j}$,
    ]
    \modelboxplot{lstm-3_ppl}{violet}{0.2}
    \modelboxplot{transformer-3_ppl}{teal}{-.2}
  \end{axis}
\end{tikzpicture}
\caption{
  Average model performance by community.
  The boxes indicate 90 percent confidence intervals. Bars indicate ... TODO:. The outliers are shown as dots.
   See also table 1 in the supplementary materials
   for a tabular version of these results with community names.
}
\label{fig:comm-stratified-box}
\end{figure}

@@

We can characterize the quality\jp{performance} of the LMCC with a confusion matrix
$C$, defined by $C_{ij} = P(c=c_i \mid m)$ for a given (test set) message $m$ 
from community $c_j$.
\[C_{ij} = \avg_{m\in M_j}P(c=c_i \mid m)\]
We observe that the diagonal is clearly above the rest: on average the LMCC generally
picks assigns the highest probability to the community where a message originates (\cref{fig:confusion}).
